resistanceModelNotesAndy

### 2016-02-12 paper1_results_figs.Rmd
added curtis inputs line to plots

# Figures for paper 1 
# version 3 - in progress

@@

  #remember these don't have new exposure column
  load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

# ex10000 runs showed effect of selection    
#   load(file=paste0(outFolder,'listOutMix_ex10000.rda'))
#   load(file=paste0(outFolder,'listOutI1_ex10000.rda'))
#   load(file=paste0(outFolder,'listOutI2_ex10000.rda'))

@@

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i))
  }

@@

>>>>

# Figures for paper 1 
# version 4 - in progress

@@

  load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

  # load(file=paste0(outFolder,'listOutMix_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_1000.rda'))

# very quick test data
  # load(file=paste0(outFolder,'listOutMix_ex2_3.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_3.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_3.rda'))

@@

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "selection_coef_allele1"=0.23,
                             "selection_coef_allele2"=0.43,
                             "maleExposureProp"=1,
                             "correctMixDeployProp"=1,
                             "resist_start_hi_div_lo"=1,
                             "resist_start_1_div_2"=1)

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

@@

# Some examples showing how changing effectiveness can alter the ranking of insecticide strategies
### Curtis' Fig 2. inputs : mix2 > combined > mix1 > seq
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### decrease effectiveness of I2 from 1 to 0.85 : mix2 > combined > seq > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > combined > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```
